Revisiting the hydrodynamic modulation of short surface waves by longer waves

### 2024-10-19 paper.tex
Fix typo
Fix typos

\begin{abstract}
Hydrodynamic modulation of short ocean surface waves by longer ambient waves is
a well-known ocean surface process that affects remote sensing, the
interpretation of \textit{in situ} wave measurements, and numerical wave
forecasting.
In this paper, we revisit the linear wave theory and derive higher-order
steady solutions for the change of short-wave wavenumber, action density, and
gravitational acceleration due to the presence of longer waves.
We validate the analytical solutions with numerical simulations of the full wave
crest and action conservation equations.
The nonlinear analytical solutions of short-wave wavenumber, amplitude, and
steepness modulation significantly deviate from the linear analytical solutions
of \citet{longuet1960changes}, and are similar to the nonlinear numerical
solutions by \citet{longuet1987propagation} and \citet{zhang1990evolution}.
The short-wave steepness modulation is attributed to be 5/8 due to the
wavenumber, 1/4 due to the wave action, and 1/8 due to the effective gravity.
We further examine the result of \citet{peureux2021unsteady} who found through
numerical simulations that the short-wave modulation grows unsteadily with
each long-wave passage.
We show that this unsteady growth only occurs only for homogeneous initial
conditions as a special case and does not generally occur, for example in more
realistic long-wave groups.
The proposed steady solutions are a good approximation of the fully
nonlinear numerical solutions in long-wave steepness up to $\approx$0.2.
Except for a subset of initial conditions, the solutions to the fully nonlinear
crest-action conservation equations are mostly steady in the reference frame of
the long waves.
\end{abstract}

@@

\begin{table}
\begin{center}
\def~{\hphantom{0}}
\begin{tabular}{cccccc}
Reference   & Analysis   & Gravity & Nonlinear  & Nonlinear   & Solution \\
            & frameworks & varies  & long waves & short waves &          \\
\hline
\citet{longuet1960changes} & Velocity potential  & No  & No  & No  & Analytical \\
\hline
\citet{phillips1981dispersion} & Crest and action & Yes & Yes & No  & Numerical \\
                               & conservation     &     &     &     &           \\
\hline
\citet{longuet1987propagation} & Velocity potential & Yes & Yes & No  & Numerical \\
\hline
\citet{henyey1988energy} & Hamiltonian & Yes & Yes & No  & Analytical \\
\hline
\citet{zhang1990evolution} & Schr\" odinger & Yes & Yes & Yes & Numerical \\
\hline
\citet{peureux2021unsteady} & Crest and action & Yes & No  & No  & Numerical \\
                            & conservation     &     &     &     &           \\
\hline
This paper  & Crest and action & Yes & Yes & No  & Analytical \\
            & conservation     &     &     &     & and numerical \\
\hline
\end{tabular}
\caption{
  Non-exhaustive summary of prior and present (this paper) approaches to
  calculating the modulation of short waves by long waves.
}
\label{table:modulation_literature_summary}
\end{center}
\end{table}

@@

\begin{equation}
\label{eq:gravity_modulation_general_stokes}
\frac{\widetilde{g}}{g}
  = \cos{\alpha} 
  + \dfrac{\partial W_{z=\eta_{St}}}{\partial t} \cos{\alpha_{St}}
  + \dfrac{\partial U_{z=\eta_{St}}}{\partial t} \sin{\alpha_{St}}
\end{equation}

>>>>

\begin{abstract}
Hydrodynamic modulation of short ocean surface waves by longer ambient waves is
a well-known ocean surface process that affects remote sensing, the
interpretation of \textit{in situ} wave measurements, and numerical wave
forecasting.
In this paper, we revisit the linear wave theory and derive higher-order
steady solutions for the change of short-wave wavenumber, action density, and
gravitational acceleration due to the presence of longer waves.
We validate the analytical solutions with numerical simulations of the full wave
crest and action conservation equations.
The nonlinear analytical solutions of short-wave wavenumber, amplitude, and
steepness modulation significantly deviate from the linear analytical solutions
of \citet{longuet1960changes}, and are similar to the nonlinear numerical
solutions by \citet{longuet1987propagation} and \citet{zhang1990evolution}.
The short-wave steepness modulation is attributed to be 5/8 due to the
wavenumber, 1/4 due to the wave action, and 1/8 due to the effective gravity.
We further examine the result of \citet{peureux2021unsteady} who found through
numerical simulations that the short-wave modulation grows unsteadily with
each long-wave passage.
We show that this unsteady growth only occurs for homogeneous initial
conditions as a special case and does not generally occur, for example in more
realistic long-wave groups.
The proposed steady solutions are a good approximation of the fully
nonlinear numerical solutions in long-wave steepness up to $\approx$0.2.
Except for a subset of initial conditions, the solutions to the fully nonlinear
crest-action conservation equations are mostly steady in the reference frame of
the long waves.
\end{abstract}

@@

\begin{table}
\begin{center}
\def~{\hphantom{0}}
\begin{tabular}{cccccc}
Reference   & Analysis   & Gravity & Nonlinear  & Nonlinear   & Solution \\
            & framework & varies  & long waves & short waves &          \\
\hline
\citet{longuet1960changes} & Velocity potential  & No  & No  & No  & Analytical \\
\hline
\citet{phillips1981dispersion} & Crest and action & Yes & Yes & No  & Numerical \\
                               & conservation     &     &     &     &           \\
\hline
\citet{longuet1987propagation} & Velocity potential & Yes & Yes & No  & Numerical \\
\hline
\citet{henyey1988energy} & Hamiltonian & Yes & Yes & No  & Analytical \\
\hline
\citet{zhang1990evolution} & Schr\" odinger & Yes & Yes & Yes & Numerical \\
\hline
\citet{peureux2021unsteady} & Crest and action & Yes & No  & No  & Numerical \\
                            & conservation     &     &     &     &           \\
\hline
This paper  & Crest and action & Yes & Yes & No  & Analytical \\
            & conservation     &     &     &     & and numerical \\
\hline
\end{tabular}
\caption{
  Non-exhaustive summary of prior and present (this paper) approaches to
  calculating the modulation of short waves by long waves.
}
\label{table:modulation_literature_summary}
\end{center}
\end{table}

@@

\begin{equation}
\label{eq:gravity_modulation_general_stokes}
\frac{\widetilde{g}}{g}
  = \cos{\alpha_{St}}
  + \dfrac{\partial W_{z=\eta_{St}}}{\partial t} \cos{\alpha_{St}}
  + \dfrac{\partial U_{z=\eta_{St}}}{\partial t} \sin{\alpha_{St}}
\end{equation}
